%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX CV for Michael Dingler 2020
% Original authors:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolors' to disable colors in section headers
\documentclass[]{friggeri-cv-a4}
\pagecolor{fantastic1}
\addbibresource{bibliography.bib} % Specify the bibliography file to include publications
%\usepackage[german]{babel}
\begin{document}

\header{michael}{dingler}{software developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{core facts}
Michael Helmut Dingler
~
German citizen
born 1977-12-09 in Rosenheim
\section{contact}
Schmuckerweg 6
81825 Munich
Germany
~
(0176) 555-17721
~
\href{mailto:mhd@gmx.com}{mhd@gmx.com}
\href{http://twitter.com/mhd}{twitter.com/mhd}
\section{languages 1}
German - native
English - fluent
\section{languages 2}
Javascript \& TypeScript
Perl, Python, Ruby, Tcl
Java, Objective-C, C, C++
\section{tools \& apis}
DBMS (SQL, PL/SQL, ORMs)
Interfaces (REST, SOAP, etc.)
adv. Unix knowledge
CSS \& HTML, React, ExtJs
UI \& UX, MFC, Swing, Tk
\section{interests}
history, pop psychology,
music, RPGs,
hiking \& biking
anglo- and cinephile,
bookworm
\end{aside}

% Arbeit

\section{work experience}

%\subsection{Full Time}

% \begin{entrylist}
% \entry
% {2012--}
% {LEHMAN BROTHERS}
% {Los Angeles, California}
% {\emph{1\textsuperscript{st} Year Analyst} \\
% Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping. \\
% Detailed achievements:
% \begin{itemize}
% \item Learned how to make amazing coffee
% \item Finally determined the reason for \textsc{PC LOAD LETTER}:
% \begin{itemize}
% \item Paper jam
% \item Software issues:
% \begin{itemize}
% \item Word not sending the correct data to printer
% \item Windows trying to print in letter format
% \end{itemize}
% \item Coffee spilled inside printer
% \end{itemize}
% \item Broke the office record for number of kitten pictures in cubicle
% \item Learned how to make more amazing coffee on a new machine
% \end{itemize}}
% \end{entrylist}

\begin{entrylist}
\entry
{2012--}
{direkt + online, Munich}
{Perl, JavaScript, TypeScript, Postgres, iOS}
{\emph{Software Developer/Architect} \\
Full stack developer of a direct marketing system, address and permission management, web shop, data import and export, reporting, target group selection, native mobile applications (iOS). Deployment and DevOps tasks for the system. Team lead nearshoring. General architecture and product owner tasks.}
\end{entrylist}


\begin{entrylist}
\entry
{2008--2011}
{EPAC, Rosenheim/Edison, NJ}
{Java, Oracle, C++, PLCs, Python}
{\emph{Software Engineer} \\
Maintenance and management of a print-on-demand (POD) system during first production run. Participation in developing a custom replacement for said system, including control of production workflow and prepress. Extended stays in USA.}
\end{entrylist}


\begin{entrylist}
\entry
{2008}
{Red Moon Studios, Augsburg}
{PHP, MySQL}
{\emph{Software Developer} \\
Development and maintenance of a family of browser-based online multi-player games.}
\end{entrylist}


\begin{entrylist}
\entry
{2007--2008}
{GMX, Munich}
{Java, J2EE}
{\emph{Software Developer} \\
Development and extensions of news portal applications and adware.}
\end{entrylist}


\begin{entrylist}
\entry
{2004--2007}
{Cenit, Munich}
{Unix, ksh, Java, Swing, PHP, Tcl, Python}
{\emph{Software Engineer} \\
Software consulting for the automobile industry, e.g. automating sysadmin tasks for CAD/CAE. Main developer of a cross-platform CAE application to manage tesselation and 3D collision detection for engine parts. Development of ETL tools and tasks. Various web-based projects.}
\end{entrylist}


\begin{entrylist}
\entry
{2003--2004}
{Apple, Cork, Ireland}
{Apple products}
{\emph{Help Desk Agent} \\
First level soft- and hardware support in English and German.}
\end{entrylist}

\begin{entrylist}
\entry
{2003}
{Damitra, Freilassing}
{PHP, MySQL}
{\emph{Software Developer} \\
Design \& development of an informaton and ad delivery platform, including custom kiosk systems and central content management system.}
\end{entrylist}

\begin{entrylist}
\entry
{2000--2002}
{Consol, Munich}
{Unix, Java, Tcl, Perl, C/C++, Oracle}
{\emph{Software Consultant} \\
Software development task for various Munich-based customers, e.g. process accounting in a heterogenous Unix data center, custom CORBA bridge for telecommunication platform, various web sites \& apps.}
\end{entrylist}

\begin{entrylist}
\entry
{2000}
{Global Systems, \emph{Munich}}
{Windows, MFC, C++}
{\emph{Software Engineer} \\
Continuing development of a native Windows POS system for insurance brokers, to reflect current offers and legal structures. QA and testing this on most possible laptop configurations.}
\end{entrylist}

\section{education}
\begin{entrylist}
\entry
{1998--1999}
{University of applied Sciences Rosenheim}
{Computer Science}
{\textit{no degree, dropped out}}
\end{entrylist}
\end{document}
